Job Demands-Resources Model Components through the Lens of O*NET Classifications

### 2023-03-31 Submission.Rmd
updating implications section

Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a “resource” or “demand”. Theoretically, however, our findings support a growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal. There are individual differences in how employees experience the characteristics of their jobs.

These results have implications for practitioners as well, providing support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees’ performance. The reality that there are more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging. Somewhat surprisingly, hindrances are rated more variably. As such, one important implication is that of frequent communication with employees regarding their perceptions of characteristics that limit their performance. @lepine2005meta and @podsakoff2007differential encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands.

>>>>

The findings presented above have implications for both theory and practice. First, this research is couched within the well-studied job demands-resources theory [@demerouti2001job].We argue that while useful, additional emphasis should be placed on individual differences in perceptions of job characteristics. In fact, our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs [@webster2011extending]. This finding aligns quite well with both the transactional theory of stress and coping, and the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely [@lazarus1984stress], and thus, could appraise them as either a challenge or hindrance to their job performance [@cavanaugh2000empirical]. Further, @cavanaugh2000empirical suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes [e.g., @cavanaugh2000empirical].

Differences in outcomes depending on whether or not an employee perceives a job characteristic to be a challenge or hindrance has practical implications. Our results suggest that what is generally seen as a resource and challenge tends to be somewhat agreed upon. As such, managers and supervisors can predict with some confidence which characteristics are perceived as supportive to employees’ performance. Somewhat surprisingly, hindrance demands are rated more variably and thus, it may be important to have conversations about job characteristics and expectations at multiple time points after hire. Specifically, having conversations with employees regarding their perceptions of characteristics that limit their performance is important. Such conversations could happen during an annual performance review or more informally. In addition, @lepine2005meta and @podsakoff2007differential encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands, which may be associated with increased performance in the short term, but strain when prolonged.
